### 2022-09-14 chapters/literature/draft_citations.tex
add :  runtime soa

@@

% hotspot vs J9 \cite{oi2011power} - same but for big querries \cite{chiba2018towards}

% infer the energy cost based on the byte code instructions \cite{ma2017biogeography}

@@

The aim of this work is to present a set of guidelines to create a benchmarking system to to measure the energy consumption of different programs.
After that, we will use this system to compare the energy consumption of different programming languages. We will extend the work of \citeauthor{pereira2017energy} to a closer distance to production environment by comparing a set of use cases.
Starting by GRPC framework, and a set of Web Frameworks.
Finally, we will discuss the impact of the execution environment on the energy consumption of two of the most famous programming languages Java and Python and present how can tunning the Virtual Machine can reduce the energy consumption.

>>>>

Besides the impact of the orchestration of virtual machine, some works have been targeting the runtime of specific programming languages.Using the TPC-DS benchmark  , \citeauthor{chiba2018towards} investigated the influence of HOTSPOT \footnote\url{https://openjdk.org/groups/hotspot/} and J9\footnote{\url{https://www.eclipse.org/openj9/}} on the performance of SQL-on-Hadoop systems (SPARK and TEZ) to reveal a three-fold disadvantage that one JVM can have over the other\cite{chiba2018towards}.
\citeauthor{oi_power_2011} also compared the performance of HOTSPOT and J9. They demonstrated in their research~\cite{oi_power_2011} that the relative performance of a JVM is affected by the workload. They discovered that HOTSPOT's performance ranged from 44\% to 289\% of J9, while its dynamic power consumption ranged from 2.7W to 7.2W, using the SPECjvm2008~\cite{shiv2009specjvm2008} benchmarks.

As for python, \citeauthor{redondo_comprehensive_2015}compared the performance and memory usage of various Python implementations (CPython, Jython, IronPython, PyPy, and so on) using a 215 set of benchmarks to discover that Python2 performed better with short applications, while Python3 versions covered more tests due to compatibility and the fact that Python2 became obsolete.\cite{redondo_comprehensive_2015}.

@@

@@

The aim of this work is to present a set of guidelines to create a benchmarking system to to measure the energy consumption of different programs.
After that, we will use this system to compare the energy consumption of different programming languages. We will extend the work of \citeauthor{pereira_energy_2017} to a closer distance to production environment by comparing a set of use cases.
Starting by GRPC framework, and a set of Web Frameworks.
Finally, we will discuss the impact of the execution environment on the energy consumption of two of the most famous programming languages Java and Python and present how can tunning the Virtual Machine can reduce the energy consumption.
